
# Course Proyect
## Loading and preprocessing the data

For processing data, first, We go to load the data from [https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip]

```{r}
file = "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(file,destfile = "activity.zip",method = "curl")
unzip("activity.zip")
act <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

```{r, echo=TRUE}
library(dplyr)
sub <- select(act, date,steps)
sub <- group_by(sub,date)
stpfday <- summarise(sub,steps = sum(steps,na.rm = TRUE))
stpfday <- as.data.frame(stpfday)
stpfday
```

The grap:
```{r, echo=TRUE}
barplot(stpfday$steps,xlab = "Date  [0-60] days",ylab = "Steps",main = "Total Number of Steps taken each day")
```

The mean and median of steps for day
```{r, echo=TRUE}
eachday <- summarise(sub,meanfday = mean(steps,na.rm = TRUE),medianfday = median(steps,na.rm = TRUE))
eachday <- as.data.frame(eachday)
eachday
```
## What is the average daily activity pattern?

```{r, echo=TRUE}
meanday <- eachday$meanfday
meanday[is.nan(meanday)] <- 0
plot(1:length(stpfday$date),meanday,type = "l",xlab = "Interval for Days",ylab = "Averaged across all days",main = "The Average daily activity pattern")
```

Max. steps
```{r, echo=TRUE}
maxMeanSteps <- max(eachday$meanfday,na.rm = TRUE)
results <- eachday[c(1,2)][eachday[2] == maxMeanSteps]
results <- results[!is.na(results)]
results
```

## Imputing missing values
```{r, echo=TRUE}
missingValues <- is.na(act$steps)
missingValues <- summary(missingValues)[[3]]
#
missingValues
```

Change of values "NA" to "0"
```{r, echo=TRUE}
act2 <- act
act2[1][is.na(act2$steps),] <- 0
```
New dataset 
```{r}
head(act2)
```

The grap ~ grap before
```{r}
sub2 <- select(act2, date,steps)
sub2 <- group_by(sub2,date)
stpfday2 <- summarise(sub2,steps = sum(steps))
stpfday2 <- as.data.frame(stpfday)
barplot(stpfday2$steps,xlab = "Date  [0-60] days",ylab = "Steps",main = "Total Number of Steps taken each day")
```
and the mean and the median 
```{r}
eachday2 <- summarise(sub2,meanfday = mean(steps),medianfday = median(steps))
eachday2 <- as.data.frame(eachday2)
eachday2
```
## Are there differences in activity patterns between weekdays and weekends?
Yes, there are differences.
Show the new datasets
```{r}
dates <- as.Date(act$date)
weekd <- c(1:length(dates))
for(i in 1:length(dates)){
    if(weekdays(dates[i]) == "sábado" | weekdays(dates[i]) == "domingo"){
        weekd[i] <- "Weekend"
    }else{ weekd[i] <- "Weekday"}    
}
weekd <- factor(weekd,levels = c("Weekend","Weekday"))
act <- cbind(act,as.data.frame(weekd))
head(act)
```

Show the grap

```{r}
dat1<- act%>%
        filter(weekd =="Weekday")
dat2<- act%>%
        filter(weekd =="Weekend")
#
par(mfrow = c(2,1))
plot(dat1$interval,dat1$steps,type = "l",xlab = "Interval", ylab = "Steps")
plot(dat2$interval,dat2$steps,type = "l",xlab = "Interval", ylab = "Steps")
```

```{r echo=FALSE}
dev.off()